\thetitle

### 2021-05-14 writing/trail-example-table.tex
trails example: A few more small touches

  \newcommand\config[1]{\begin{minipage}{0.09\textwidth}\centering\includegraphics[width=\linewidth]{Images/#1}\end{minipage}}
  \newcommand\runtimeError{\begin{minipage}{0.03\textwidth}\centering\includegraphics[width=\linewidth]{Images/runtime-error}\end{minipage}}
  \newcommand\checkFailure{\begin{minipage}{0.03\textwidth}\centering\includegraphics[width=\linewidth]{Images/check-failure-plain}\end{minipage}}
  \newcommand\blameFinger{\begin{minipage}{0.02\textwidth}\centering\vspace{0.25em}\includegraphics[width=\linewidth]{Images/finger}\end{minipage}}
  \newcommand\typeError{\scalebox{1.5}{$\tau_{\hspace{-0.1em}\times}$}}
  \newcommand\success{\textcolor{black!30!green}{\checkmark}}
  \newcommand\fail{\textcolor{red}{\sffamily x}}
  \footnotesize
\centering
\begin{tabular}{l|ccl|ccl|cc|c}
\multicolumn{3}{c}{\begin{minipage}{0.25\textwidth}\centering\includegraphics[width=\linewidth]{Images/take5-module-graph}\end{minipage}} &
\multicolumn{7}{c}{\begin{minipage}{0.69\textwidth}\centering\includegraphics[width=\linewidth]{Images/trails-example}\end{minipage}} \\
\multicolumn{3}{c}{\begin{minipage}{0.25\textwidth}\centering the dependency graph\end{minipage}} &
\multicolumn{7}{c}{\begin{minipage}{0.69\textwidth}\centering the paths taken by each mode through the configuration lattice\end{minipage}} 
\vspace{1em} \\
\end{tabular}

@@

\noindent{\bf config} Each box corresponds to a module and indicates (with x) if it is typed. 
The mutated module is gray.

@@

\noindent{\bf result}\\
\begin{center}
\vspace{-2.5em}
\begin{tabular}{l@{\quad}l}
symbol        & denotation \\ \hline 
\blameFinger  & the configuration signals a dynamic type check failure, blaming the module(s) below \\
\typeError    & the configuration does not type check\\
\runtimeError & the configuration fails a check by the runtime system\\
\checkFailure & the configuration signals a dynamic type check failure for which blame is ignored\\
\end{tabular}
\end{center}

>>>>

  \newcommand\config[1]{\begin{minipage}{0.09\textwidth}\centering\includegraphics[width=\linewidth]{Images/#1}\end{minipage}}
  \newcommand\runtimeError{\begin{minipage}{0.03\textwidth}\centering\includegraphics[width=\linewidth]{Images/runtime-error}\end{minipage}}
  \newcommand\checkFailure{\begin{minipage}{0.03\textwidth}\centering\includegraphics[width=\linewidth]{Images/check-failure-plain}\end{minipage}}
  \newcommand\blameFinger{\begin{minipage}{0.02\textwidth}\centering\vspace{0.25em}\includegraphics[width=\linewidth]{Images/finger}\end{minipage}}
  \newcommand\typeError{\scalebox{1.5}{$\tau_{\hspace{-0.1em}\times}$}}
  \newcommand\success{\textcolor{black!30!green}{\checkmark}}
  \newcommand\fail{\textcolor{red}{\sffamily x}}
  \footnotesize
\centering
\begin{tabular}{l|ccl|ccl|cc|c}
\multicolumn{3}{c}{\begin{minipage}{0.25\textwidth}\centering\includegraphics[width=\linewidth]{Images/take5-module-graph}\end{minipage}} &
\multicolumn{7}{c}{\begin{minipage}{0.69\textwidth}\centering\includegraphics[width=\linewidth]{Images/trails-example}\end{minipage}} \\
\multicolumn{3}{c}{\begin{minipage}{0.25\textwidth}\centering the dependency graph\end{minipage}} &
\multicolumn{7}{c}{\begin{minipage}{0.69\textwidth}\centering the paths taken by each mode through the configuration lattice\end{minipage}} \\
\end{tabular}
\vspace{1em}

@@

\noindent{\bf config} \hspace{0.5em} Each box corresponds to a module and indicates (with x) if it is typed. 
The mutated module is gray.

@@

\noindent{\bf result}\\
\begin{center}
\vspace{-2.5em}
\begin{tabular}{c@{\quad}l}
symbol        & denotation \\ \hline 
\blameFinger  & the configuration signals a dynamic type check failure, blaming the module(s) below \\
\typeError    & the configuration does not type check\\
\runtimeError & the configuration fails a check by the runtime system\\
\checkFailure & the configuration signals a dynamic type check failure for which blame is ignored\\
\end{tabular}
\end{center}
